Syntax and Semantics of Abstract Binding Trees

### 2015-12-31 paper.tex
mention strengthening; move explanation of symbols sheaf (#42)

Returning to the site $\SCtxSite$, we will write $\mathbf{S}_\tau$ for the sheaf
of symbols of sort $\tau$, a subobject of the Yoneda embedding of the empty
symbol context, $\Yoneda{\cdot}$.

@@

We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators_a(\Upsilon)}$; note that this judgment enjoys
the structural properties of weakening and exchange via functoriality of
$\Operators$. An operator signature is defined by specifying, for each arity
$a$, the sheaf $\Operators_a$, whose ``elements'' are the operators of arity
$a$.

@@

These rules correspond to the following family of sheaves:
\begin{align*}
  \ADefine{
    \Operators_{
      \MkArity{
        \MkValence{}{}{\SortExp},
        \MkValence{\SortExp}{}{\SortExp}
      }{
        \SortExp
      }
    }
  }{
    \mathbb{1}
  }\\
  \ADefine{
    \Operators_{
      \MkArity{}{\SortExp}
    }
  }{
    \mathbf{S}_\SortExp
  }\\
  \ADefine{
    \Operators_{
      \MkArity{
        \MkValence{}{}{\SortExp}
      }{
        \SortExp
      }
    }
  }{
    \mathbf{S}_\SortExp
  }
\end{align*}

>>>>

@@

We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators_a(\Upsilon)}$; note that this judgment enjoys
the structural properties of weakening and exchange via functoriality of
$\Operators$, and strengthening via the sheaf condition. An operator signature
is defined by specifying, for each arity $a$, the sheaf $\Operators_a$, whose
``elements'' are the operators of arity $a$.

@@

Let $\mathbf{S}_\tau$ be the sheaf of symbols of sort $\tau$, a subobject of
the Yoneda embedding of the empty symbol context, $\Yoneda{\cdot}$:
\[
  \Define{\mathbf{S}_\tau(\Upsilon)}{
    \MkSet{
      u\in\Dom{\Upsilon}
      \mid
      \Upsilon(u) \equiv \tau
    }
  }
\]
%
Then the above rules correspond to the following family of sheaves:
\begin{align*}
  \ADefine{
    \Operators_{
      \MkArity{
        \MkValence{}{}{\SortExp},
        \MkValence{\SortExp}{}{\SortExp}
      }{
        \SortExp
      }
    }
  }{
    \mathbb{1}
  }\\
  \ADefine{
    \Operators_{
      \MkArity{}{\SortExp}
    }
  }{
    \mathbf{S}_\SortExp
  }\\
  \ADefine{
    \Operators_{
      \MkArity{
        \MkValence{}{}{\SortExp}
      }{
        \SortExp
      }
    }
  }{
    \mathbf{S}_\SortExp
  }
\end{align*}
